Automatic Matching of Bullet Lands

### 2016-07-19 revision/response.Rmd

***We selected random forests because the method has desirable attributes and can be easily ported to other forensic applications. We were not intending to provide new insights on random forests. The focus of the paper was to show the potential of combining a large number ofimage attributes to discriminate among bullets. As the forest ultimately predicted every land-to-land comparison properly, we felt that a comparison to other learning methods was outside the scope of this paper. Had a wider variety of data been available, there would likely be more variability in the predictions and a comparison to other learning methods would be prudent.***

# Reviewer B

4. The authors should discuss their work in the context of Nicholas Petraco’s work as well as other ongoing research endeavors in impression and pattern evidence. See https://www.ncjrs.gov/pdffiles1/nij/grants/239048.pdf The alignment method should have been compared with a standard method- See Patraco’s NIJ report for a couple of examples. As presented the novel component of the paper is the "twicing" for grooves combined with a loess fit to the remove curves from bullet images. I am not sure this is the authors intention. It would be interesting to compare this method with some of the classical methods from functional data analysis used for curve registration.

***TODO: Check which references are and are not in the paper. Add Chu 2010, Chu 2009, Bachrach 2002, Vorburger 2011, Riva 2014. Cite Bachrach 2006 in response to reviewer about barrel effects***

@@

# Reviewer C

13. there is a lack of knowledge of the existing literature on statistical work performed on tool marks and firearms. For example, the work performed by Nicholas Petraco, Fabiano Riva, or Alan Zheng in the past 5 years is not mentioned. Instead, old research projects are mentioned, which mostly focus on manual identification. The authors need to discuss the novelty of their method (and how it potentially addresses the shortcomings of these recent methods)

***The point that the reviewer makes is valid.  While we were familiar with the computer-assisted approaches that have been proposed, practice still relies on human examination of potential candidates presented by a system such as NIBIN. We have added what we hope is an acceptably complete review of the literature in the revised manuscript.***

***TODO: Cite riva paper, explain work has been done on cartridges (not bullets). Cite John Song's papers***

### 2016-07-25 imaging-paper.Rnw
Reproducible research comments

The purpose of our paper is to present an automatic matching routine that allows for a completely objective assessment of the quality of a match. \eh{We have chosen to perform the matching on a land-to-land level, rather than bullet-to-bullet. Although doing so introduces an implicit assumption of independence between lands, assuming independence only serves to make the task more challenging. XXX need more?}
The original paper on the complete Hamby study already reports the successful use of several computer-assisted methods; aside from a zero false positive rate, no further details on a false-negative error rate for bullets are given nor are error rates for land-to-land matches mentioned. 
% Hamby study: automated systems were successfully used for matching:
%  Intelligent Automation's SciClops - Dr. Ben Bachrach (Maryland, United States);
% Automated Land Identification System (ALIS) - Mr. Tsuneo Uchiyama (Tokyo, Japan);
% Integrated Ballistics Identification System (IBIS) – Mr. Robert Thompson (California, United States);
% BulletTRAX-3DTM - Forensic Technology Scientists (Montreal, Canada) (2 sets)

>>>>

The purpose of our paper is to present an automatic matching routine that allows for a completely objective assessment of the quality of a match. Our algorithm is fully open source and available on GitHub \citep{x3prplus}. This transparency allows for a greater understanding of the individual steps involved in the bullet matching process, and allows other forensic examiners, as well as outside observers, examine the factors that separate known bullet matches from non-matches. We have chosen to perform the matching on a land-to-land level, rather than bullet-to-bullet. Although doing so introduces an implicit assumption of independence between lands, assuming independence only serves to make the task more challenging.
The original paper on the complete Hamby study already reports the successful use of several computer-assisted methods; aside from a zero false positive rate, no further details on a false-negative error rate for bullets are given nor are error rates for land-to-land matches mentioned. 
% Hamby study: automated systems were successfully used for matching:
%  Intelligent Automation's SciClops - Dr. Ben Bachrach (Maryland, United States);
% Automated Land Identification System (ALIS) - Mr. Tsuneo Uchiyama (Tokyo, Japan);
% Integrated Ballistics Identification System (IBIS) – Mr. Robert Thompson (California, United States);
% BulletTRAX-3DTM - Forensic Technology Scientists (Montreal, Canada) (2 sets)
